### 2012-05-12 trunk/GUIErrorDetector/paper/evaluation.tex
tweak

%After checking against existing patches, we found
%Our tool correctly identified the \oldbugs known errors, as compared to
%their patches.
We submitted all \newbugs new errors
to the respective developers. As of April 2012, 
we have reproduced 3 errors, the S3dropbox developers have confirmed
1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
have not yet been verified by the developers.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
However, the number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible for this variant to enumerate all paths for a realistic
call graph, which often contains thousands of
nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
we ran this variant on each subject for 1 hour, it explored 4.9$\times$$10^9$ paths on average, but did not
output any real errors before it terminated.

>>>>

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error S3dropbox has been confirmed, we have reproduced 2 errors,
and 4 errors in VirgoFTP, FileBunker, and ArecaBackup
have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.
All found bugs and our experimental results are
publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
However, the number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible for this variant to enumerate all paths for a realistic
call graph, which often contains thousands of
nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
we ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths on average, but did not
output any real errors before it terminated.
